Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-02 wearables_survey.tex
Finally got methodology section and results intro looking right.

@@

\section{Results}
After removing 465 incomplete responses, our sample consisted of 1,785 participants. Of these X, A\% were male, with a median age of B. Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

MENTION VUR AND WHY WE USED IT.

%confusing runthrough of the results.. is this too packed? 
%Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.  Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public. Although in some cases, asking about wearables or smart phones did elicit unique reactions to the situation from participants, the device generally does not contribute to the severity of the threat. When assessing new technologies as a whole, participants assessed many of the new technologies similarly as low risk and low benefit. Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.

Write about what is commented out above, but as a ROADMAP.

>>>>

\subsection{Analysis}
After removing 465 incomplete responses, our sample consisted of 1,785 participants. Of these X, A\% were male, with a median age of B. For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale. The VUR also does not presume that the ratings, ranging from indifferent to very upset, are linearly spaced. Additionally, we believe that everyone would be upset at least a little bit at the given scenarios, in which an device takes action without permission. Therefore, we believe that the main distinguishing factor of a participant reacting to a given situation is if they are maximally upset or not, rather than how upset they were. Although participants gave a wide range of numbers (i.e. a participant who answered that one technology was six orders of magnitude more beneficial than another), we do not normalize the numerical responses for the risk/benefit analysis. Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers. Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

@@

\section{Results}
%confusing runthrough of the results.. is this too packed? 
%Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.  Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public. Although in some cases, asking about wearables or smart phones did elicit unique reactions to the situation from participants, the device generally does not contribute to the severity of the threat. When assessing new technologies as a whole, participants assessed many of the new technologies similarly as low risk and low benefit. Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.

In this section, we present the results of our multiple-part survey. We first discuss which <data>, <recipient>, and <device> types contributed to how threatening a situation was perceived by a participant. We follow this discussion with a regression model which discusses all of the factors which may have contributed to a participant being very upset at a given situation, including <data>, <recipient>, and <device> types, but also with respect to demographics questions. Next, we discuss the participants' risk/benefit assessment of various new technologies with respect to well-known, existing technologies. We conclude the section with participants self-reported concerns about the biggest risks in owning a wearable device.
